---
title: "BigDots"
author: "Daniel Newman"
date: "12 June 2016"
output:
  html_document:
    fig_width: 8
    keep_md: yes
  word_document: default
---

```{r Load and Pre-Process the single trial Data, echo=FALSE, include=FALSE}

####Which computer/directory is this being run on?
location<-"Monash"
# location<-"GersLaptop"

if (location=="Monash") {
    setwd(("C:/GitHub/big_dots/Analyses Scripts_R"))
} else if (location=="GersLaptop") {
    setwd(("C:/Users/loughnge/Documents/GitHub/big_dots/Analyses Scripts_R"))
} else setwd(("~"))



####################################
#######  How to use ################
####################################

# 1) Install the packages and software specified below. (consider also updating all installed packages by chosing Update on the Packages tab)
# 2) Set the working directory (setwd) above, and directory where you have "data_ParticipantLevel", "master_matrix_R" and "ID_vector" saved
# 3) Hit Knit Word (or Knit HTML)! (Output can take while due to bootstrapping the robust effect size and calculating the Bayesian Highest Density Iinterval)


####################################
######  FIRST TIME ONLY ############
####################################

#Remove # in front of the line below and run the code. Replace the # after installing the packages, otherwise the R markdown script will give errors.

# install.packages(c("MASS", "akima", "robustbase", "cobs", "robust", "mgcv", "scatterplot3d", "quantreg", "rrcov", "lars", "pwr", "trimcluster", "mc2d", "psych", "Rfit","MBESS", "BayesFactor", "PoweR", "ggplot2", "reshape2", "plyr", "devtools", "rmarkdown","gmodels", "HLMdiag", "car", "gridExtra", "bootES", "BEST","foreign","nlme","pastecs","multcomp","compute.es","ez","lattice","lme4","effects","diagram","png", "grid", "dplyr","readxl", "openxlsx", "haven","schoRsch", "lubridate"))

###################################################################################################################################
## load relevant libraries 
library(foreign)
library(car)
library(nlme)
library(ggplot2)
library(pastecs)
library(psych)
library(multcomp)
library(compute.es)
library(ez)
library(lme4)
library(png)
library(grid)
library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)

###### Import single trial data:
if (location=="Monash") {
data <- read.csv("C:/GitHub/big_dots/master_matrix_R_BigDots.csv", header=FALSE)
} else if (location=="GersLaptop") {
data <- read.csv("C:/Users/Dan/Documents/GitHub/big_dots/master_matrix_R_BigDots.csv", header=FALSE)
} else setwd(("~"))
#Import IDs:
if (location=="Monash") {
ID <- read.table("C:/GitHub/big_dots/ID_vector_BigDots.csv", quote="\"")
} else if (location=="GersLaptop") {
ID <- read.table("C:/Users/Dan/Documents/GitHub/big_dots/ID_vector_BigDots.csv", quote="\"")
} else setwd(("~"))

data$ID<-data[,1]
#Replace the participant numbers with IDs:
data[,1]<-ID[,1]
#Remove the seperate ID vector now it has been included into data dataframe
rm(ID)
drops <- c("ID")
data<-data[,!(names(data) %in% drops)]


###Read in Participant Demographics (note for Sex 1=male)
Demographics<-read_excel("Participant_Demographics.xlsx") %>% #then calculate Age at testing date:
    mutate(Age_as_period=as.period(interval(Date_Of_Birth, Date_Of_Testing), units="years")) %>%
    mutate(Sex = ifelse(Sex==1, "Male", "Female"))
#Calculate Age in numeric format
Demographics$Age<-as.numeric(difftime(as.Date(Demographics$Date_Of_Testing), as.Date(Demographics$Date_Of_Birth), units = "days")/365)
summary(Demographics$Age)


#########################################################################################################################

data<- data %>% #Rename data columns:
    rename(., 
            ID=V1,
            TotalTrialNumber=V2,
            Trial=V3,
            ITI=V4,
            Hemifield=V5,
            Accuracy=V6,
            Art_neg500_0=V7,
            Art_neg100_100PR=V8,
            Art_neg500_100PR=V9,
            Art_neg100_1000=V10,
            FixBreak_neg500_0=V11,
            FixBreak_neg100_100PR=V12,
            FixBreak_neg500_100PR=V13,
            FixBreak_neg100_1000=V14,
            RT=V15,
           PreAlphaPower=V16,
           PreAlphaPowerLH=V17,
           PreAlphaPowerRH=V18,
           PreAlphaAsym=V19,
           PostAlphaPowerLH=V20,
           PostAlphaPowerRH=V21) %>% #next make the required columns into factors:
    mutate_each_(funs(factor), c("ITI", "Hemifield", "Accuracy")) %>% #next re-class required vectors into Logicals:
    mutate_at(vars(starts_with("Art_")), funs(as.logical)) %>% 
    mutate_at(vars(starts_with("FixBreak_")), funs(as.logical)) %>% #next use the ! negation operator to reverse of a TRUE/FALSE vectors: 
    mutate_if(purrr::is_logical, funs(!.)) %>% #next Rename factor Levels:
    mutate(Hemifield = ifelse(Hemifield==1, "Left", "Right"), 
           Accuracy= ifelse(Accuracy==1, "Hit", ifelse(Accuracy==2, "WrongButton", "Miss")))


Demographics <-Demographics[Demographics$ID %in% data$ID, ]   

###############Data Cleaning For Single Trial Data######################


#Check number of Trials for each participant by running the function 'length', 
#on "data$RT" for each DAT1_3UTR, broken down by ID + Light
num_trials1 <- data %>% group_by(ID) %>% summarise( Trials = length(RT))
summary(num_trials1$Trials)


##################Accuracy ##########################
Accuracy_checker <- data %>% group_by(ID) %>% 
                    summarise(Hits  = sum(Accuracy=="Hit"),
                               Misses = sum(Accuracy=="Miss" | Accuracy=="WrongButton")) %>%
                    mutate(Total=Hits+Misses,
                           Accuracy_overall= (Hits/Total)*100) 
summary(Accuracy_checker$Accuracy_overall)

##Add in overall accuracy 
data <- merge(data, Accuracy_checker, by.x = "ID", by.y = "ID")

###Remove trials where:
#RT longer than 1000ms (i.e. after target finished)
#RT faster than 100ms (i.e. too fast must be false alarm) or RT=0 (i.e. they did not respond)
#Kick out trials with fixation breaks:
data<-filter(data, RT<1500 & RT>150 & !FixBreak_neg100_100PR)


############################################ Log transform:
##############################################################################################
data$log_RT<-log(data$RT) #log
#####Z-score each participant's log_RT data ####
data$IDbyITIbyHemifield<-interaction(data$ID, data$ITI, data$Hemifield)
#calculate mean and sd 
m <- tapply(data$log_RT,data$IDbyITIbyHemifield,mean, na.rm = T)
s <- sqrt(tapply(data$log_RT,data$IDbyITIbyHemifield,var, na.rm = T))
#calculate log_RT.Z and save it inside data.frame
data$log_RT.Z <- (data$log_RT-m[data$IDbyITIbyHemifield])/s[data$IDbyITIbyHemifield]
#Remove trials where absolute log_RT.Z>3 (i.e. remove outlier RTs)
data<-data[!abs(data$log_RT.Z)>3,]


#plot again after outlier removal:
ggplot(data, aes(RT))  + geom_histogram(aes(y=..count..), colour="black", fill="white") 
ggplot(data, aes(log_RT))  + geom_histogram(aes(y=..count..), colour="black", fill="white") 


#Calculate the number of trials each participant has left after fixation break trials are kicked out:
num_trials2 <- data %>% group_by(ID) %>% summarise( Trials = length(RT))
summary(num_trials2$Trials)

#Calculate alpha desynchronisation by subtracting Pre-target Alpha from post target alpha
data$AlphaDesyncRH<-(data$PreAlphaPowerRH)-(data$PostAlphaPowerRH)
data$AlphaDesyncLH<-data$PreAlphaPowerLH-data$PostAlphaPowerLH
# Make PostAlpha contralateral (PostAlpha_c) and -Ipsilateral (PostAlpha_i) variables:
A<-data$Hemifield=="Left"
#Absolute post target alpha
data$PostAlpha_c[A]<-data$PostAlphaPowerRH[A]
data$PostAlpha_c[!A]<-data$PostAlphaPowerLH[!A]
data$PostAlpha_i[!A]<-data$PostAlphaPowerRH[!A]
data$PostAlpha_i[A]<-data$PostAlphaPowerLH[A]
#Post target Alpha desynchronisation 
data$AlphaDesync_c[A]<-data$AlphaDesyncRH[A]
data$AlphaDesync_c[!A]<-data$AlphaDesyncLH[!A]
data$AlphaDesync_i[!A]<-data$AlphaDesyncRH[!A]
data$AlphaDesync_i[A]<-data$AlphaDesyncLH[A]

rm(A)



####Import participant_level_matrix with ERP measures
if (location=="Monash") {
participant_level <- read.csv("C:/GitHub/big_dots/participant_level_matrix.csv", header=FALSE)
} else if (location=="DansLaptop") {
participant_level <- read.csv("C:/Users/Dan/Documents/GitHub/big_dots/participant_level_matrix.csv", header=FALSE)
} else setwd(("~"))
#Import IDs:
if (location=="Monash") {
ID <- read.table("C:/GitHub/big_dots/IDs.csv", quote="\"")
} else if (location=="DansLaptop") {
ID <- read.csv("C:/Users/Dan/Documents/GitHub/big_dots/IDs.csv", header=F)
} else setwd(("~"))
ID<-plyr::rename(ID,c("V1"="ID"))
participant_level$ID<-ID$ID
rm(ID)

participant_level<- participant_level %>% #Rename data columns:
                            rename(., 
                                    N2c_LeftTarget=V1,
                                    N2c_RightTarget=V2,
                                    N2i_LeftTarget=V3,
                                    N2i_RightTarget=V4,
                                    N2c_latency_LeftTarget=V5,
                                    N2c_latency_RightTarget=V6,
                                    N2i_latency_LeftTarget=V7,
                                    N2i_latency_RightTarget=V8,
                                    CPPonset_LeftTarget=V9,
                                    CPPonset_RightTarget=V10,
                                    CPPslope_LeftTarget=V11,
                                    CPPslope_RightTarget=V12) %>% #location=V13  #next calculate the ERP asymmetry measures:
                            mutate(., 
                                  N2c_Asym = (N2c_LeftTarget-N2c_RightTarget)/(N2c_LeftTarget+N2c_RightTarget), 
                                  N2i_Asym = (N2i_LeftTarget-N2i_RightTarget)/(N2i_LeftTarget+N2i_RightTarget),
                                  N2c_latency_Asym = (N2c_latency_LeftTarget-N2c_latency_RightTarget)/(N2c_latency_LeftTarget+N2c_latency_RightTarget), 
                                  N2i_latency_Asym =(N2i_latency_LeftTarget-N2i_latency_RightTarget)/(N2i_latency_LeftTarget+N2i_latency_RightTarget),
                                  CPPonset_Asym = (CPPonset_LeftTarget-CPPonset_RightTarget)/(CPPonset_LeftTarget+CPPonset_RightTarget),
                                  CPPslope_Asym = (CPPslope_LeftTarget-CPPslope_RightTarget)/(CPPslope_LeftTarget+CPPslope_RightTarget)
                                  )
# location = ifelse(location==1, "TCD", "Monash")

####################################################################################
#Collapse each participant's PreAlpha trials to participant level
PreAlphaAsym_collapsed<- data %>% 
            filter(!Art_neg500_0, !FixBreak_neg500_0) %>%
            group_by(ID) %>%
            summarise(PreAlphaAsym=mean(PreAlphaAsym))
#Merge it in with the ERP measures
participant_level<-merge(participant_level, PreAlphaAsym_collapsed, by.x = "ID", by.y = "ID") 

#Collapse each participant's PostAlpha trials to participant level
PostAlphaAsym_collapsed<- data %>% 
            filter(!Art_neg500_0, !FixBreak_neg500_0) %>%
            mutate(PostAlphaAsym=(PostAlpha_c-PostAlpha_i)/(PostAlpha_c+PostAlpha_i)) %>% #contra - ipsi asym
            group_by(ID) %>%
            summarise(PostAlphaAsym=mean(PostAlphaAsym))
#Merge it in with the ERP measures
participant_level<-merge(participant_level, PostAlphaAsym_collapsed, by.x = "ID", by.y = "ID") 


#Collapse each participant's Post-target AlphaDesync single trials to participant level
AlphaDesync_c_collapsed<- data %>% 
            filter(!Art_neg500_100PR, !FixBreak_neg500_100PR) %>%
            group_by(ID, Hemifield) %>%
            summarise(AlphaDesync_c=mean(AlphaDesync_c)) %>% #next bring Target-Hemifield up into wide format:
            spread(Hemifield, AlphaDesync_c) %>% #next rename
            rename(AlphaDesync_c_LeftTarget=Left, AlphaDesync_c_RightTarget=Right) %>% # next Calculate RT asymmetry:
            mutate(AlphaDesync_c_Asym=(AlphaDesync_c_LeftTarget-AlphaDesync_c_RightTarget)/(AlphaDesync_c_LeftTarget+AlphaDesync_c_RightTarget)) 
#Merge it in with the ERP measures
participant_level<-merge(participant_level, AlphaDesync_c_collapsed, by.x = "ID", by.y = "ID") 

AlphaDesync_i_collapsed<- data %>% 
            filter(!Art_neg500_100PR, !FixBreak_neg500_100PR) %>%
            group_by(ID, Hemifield) %>%
            summarise(AlphaDesync_i=mean(AlphaDesync_i)) %>% #next bring Target-Hemifield up into wide format:
            spread(Hemifield, AlphaDesync_i) %>% #next rename
            rename(AlphaDesync_i_LeftTarget=Left, AlphaDesync_i_RightTarget=Right) %>% # next Calculate RT asymmetry:
            mutate(AlphaDesync_i_Asym=(AlphaDesync_i_LeftTarget-AlphaDesync_i_RightTarget)/(AlphaDesync_i_LeftTarget+AlphaDesync_i_RightTarget)) 
#Merge it in with the ERP measures
participant_level<-merge(participant_level, AlphaDesync_i_collapsed, by.x = "ID", by.y = "ID") 


#Collapse each participant's RT single trials to participant level
RT_collapsed<- data %>% 
            group_by(ID, Hemifield) %>%
            summarise(RT=mean(RT)) %>% #next bring Target-Hemifield up into wide format:
            spread(Hemifield, RT) %>% #next rename
            rename(RT_Left=Left, RT_Right=Right) %>% # next Calculate RT asymmetry:
            mutate(RT_Asym=(RT_Left-RT_Right)/(RT_Left+RT_Right)) 
#Merge it in with the ERP measures
participant_level<-merge(participant_level, RT_collapsed, by.x = "ID", by.y = "ID") 


#Transform it to long format
participant_level_long<-participant_level %>%
                    gather(measure_type, data, -ID) %>%
                    na.omit()
####Find outliers in the Participant level data (abs z-score >3)####
#################################################################
#Calculate Z scores inside measure_type type TO REMOVE OUTLIERS
#Z-score each participant's data inside measure_type ####
#calculate mean and sd 
m <- tapply(participant_level_long$data,participant_level_long$measure_type,mean, na.rm = T)
s <- sqrt(tapply(participant_level_long$data,participant_level_long$measure_type,var, na.rm = T))
#calculate data.Z and save it inside participant_level_long
participant_level_long$data.Z <- (participant_level_long$data-m[participant_level_long$measure_type])/s[participant_level_long$measure_type]

#Remove trials where absolute data.Z>3 (i.e. remove outlier RTs)
# participant_level_long<-participant_level_long[!abs(participant_level_long$data.Z)>3,]


#Plot density plots again after outlier removal
ggplot(participant_level_long, aes(data))  + geom_density() + facet_wrap(~ measure_type, scales="free")

#change measure_type to factor class
participant_level_long$measure_type<-as.factor(participant_level_long$measure_type)

#Put it back into long format so I can use lapply to do t-test on columns 
participant_level<-participant_level_long %>% select(., -data.Z)  %>% 
                    spread(measure_type, data) 

#Merge in the Demographics
participant_level<-merge(participant_level, Demographics, by.x = "ID", by.y = "ID") 
####################################################################################
```


#Test the effect of Target Hemifield on RT, CPPonset, N2c, etc. using Factorial Permutation test
```{r, echo=FALSE, warning=FALSE}
###################################################################
Perm_data<- participant_level %>% 
    select(ID, RT_Left, RT_Right) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 

log <- capture.output({
   Hemifield_Perm <- ezPerm(data = Perm_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                          , perms = 1000);
 })
print("Factorial Permutation test for the effect of Hemifield on RT:")
print(Hemifield_Perm);


ggplot(Perm_data, aes(Hemifield, dv, colour = Hemifield))  + 
          geom_violin(alpha=0.5) + geom_boxplot() +  theme_bw () + geom_point()


ggplot(Perm_data, aes(Hemifield, dv, colour = Hemifield, group = ID))  + 
          geom_violin() +  theme_bw () + geom_point() + geom_line(colour="black")


###################################################################
Perm_data<- participant_level %>% 
    select(ID, CPPslope_LeftTarget, CPPslope_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 

log <- capture.output({
   Hemifield_Perm <- ezPerm(data = Perm_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                          , perms = 1000);
 })
print("Factorial Permutation test for the effect of Hemifield on CPP Slope:")
print(Hemifield_Perm);

###################################################################
Perm_data<- participant_level %>% 
    select(ID, CPPonset_LeftTarget, CPPonset_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 

log <- capture.output({
   Hemifield_Perm <- ezPerm(data = Perm_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                          , perms = 1000);
 })
print("Factorial Permutation test for the effect of Hemifield on CPP Onset:")
print(Hemifield_Perm);

ggplot(Perm_data, aes(Hemifield, dv, colour = Hemifield))  + 
          geom_violin() + geom_boxplot() +  theme_bw () + geom_point() + geom_line()

ggplot(Perm_data, aes(Hemifield, dv, colour = Hemifield, group = ID))  + 
          geom_violin() +  theme_bw () + geom_point() + geom_line(colour="black")

###################################################################
Perm_data<- participant_level %>% 
    select(ID, N2i_latency_LeftTarget, N2i_latency_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 

log <- capture.output({
   Hemifield_Perm <- ezPerm(data = Perm_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                          , perms = 1000);
 })
print("Factorial Permutation test for the effect of Hemifield on N2i_latency:")
print(Hemifield_Perm);

###################################################################
Perm_data<- participant_level %>% 
    select(ID, N2i_LeftTarget, N2i_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 

log <- capture.output({
   Hemifield_Perm <- ezPerm(data = Perm_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                          , perms = 1000);
 })
print("Factorial Permutation test for the effect of Hemifield on N2i Amplitude:")
print(Hemifield_Perm);


###################################################################
Perm_data<- participant_level %>% 
    select(ID, N2c_latency_LeftTarget, N2c_latency_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 

log <- capture.output({
   Hemifield_Perm <- ezPerm(data = Perm_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                          , perms = 1000);
 })
print("Factorial Permutation test for the effect of Hemifield on N2c_latency:")
print(Hemifield_Perm);

###################################################################
Perm_data<- participant_level %>% 
    select(ID, N2c_LeftTarget, N2c_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 

log <- capture.output({
   Hemifield_Perm <- ezPerm(data = Perm_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                          , perms = 1000);
 })
print("Factorial Permutation test for the effect of Hemifield on N2c Amplitude:")
print(Hemifield_Perm);


###################################################################
Perm_data<- participant_level %>% 
    select(ID, AlphaDesync_c_LeftTarget, AlphaDesync_c_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 

log <- capture.output({
   Hemifield_Perm <- ezPerm(data = Perm_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                          , perms = 1000);
 })
print("Factorial Permutation test for the effect of Hemifield on AlphaDesync_c:")
print(Hemifield_Perm);


###################################################################
###################################################################
Perm_data<- participant_level %>% 
    select(ID, AlphaDesync_c_LeftTarget, AlphaDesync_c_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 

log <- capture.output({
   Hemifield_Perm <- ezPerm(data = Perm_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                          , perms = 1000);
 })
print("Factorial Permutation test for the effect of Hemifield on AlphaDesync_i:")
print(Hemifield_Perm);




```


#Test the effect of Target Hemifield on RT, CPPonset, N2c, etc. using repeated measures ANOVA
```{r, echo=FALSE, warning=FALSE}
###################################################################
ANOVA_data<- participant_level %>% 
    select(ID, RT_Left, RT_Right) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 
    # %>% mutate(dv=log(dv))


   Hemifield_ANOVA <- ezANOVA(data = ANOVA_data
                        , dv = .(dv)
                        , wid = .(ID)
                        , within = .(Hemifield)
                        , within_covariates = NULL
                        , between = NULL
                        , between_covariates = NULL
                        , observed = NULL
                        , type = 3)
print("Repeated Measures ANOVA  for the effect of Hemifield on RT:")
print(Hemifield_ANOVA);



ggplot(ANOVA_data, aes(Hemifield, dv, colour = Hemifield))  + 
          geom_violin() + geom_boxplot() +  theme_bw () + geom_point()


ggplot(ANOVA_data, aes(Hemifield, dv, colour = Hemifield, group = ID))  + 
          geom_violin() +  theme_bw () + geom_point() + geom_line(colour="black")


###################################################################
ANOVA_data<- participant_level %>% 
    select(ID, CPPslope_LeftTarget, CPPslope_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 


   Hemifield_ANOVA <- ezANOVA(data = ANOVA_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                        , within_covariates = NULL
                        , between = NULL
                        , between_covariates = NULL
                        , observed = NULL
                        , type = 3);
print("Repeated Measures ANOVA  for the effect of Hemifield on CPP Slope:")
print(Hemifield_ANOVA);

###################################################################
ANOVA_data<- participant_level %>% 
    select(ID, CPPonset_LeftTarget, CPPonset_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 


   Hemifield_ANOVA <- ezANOVA(data = ANOVA_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                        , within_covariates = NULL
                        , between = NULL
                        , between_covariates = NULL
                        , observed = NULL
                        , type = 3);
print("Repeated Measures ANOVA  for the effect of Hemifield on CPP Onset:")
print(Hemifield_ANOVA);

ggplot(ANOVA_data, aes(Hemifield, dv, colour = Hemifield))  + 
          geom_violin() + geom_boxplot() +  theme_bw () + geom_point() + geom_line()

ggplot(ANOVA_data, aes(Hemifield, dv, colour = Hemifield, group = ID))  + 
          geom_violin() +  theme_bw () + geom_point() + geom_line(colour="black")

###################################################################
ANOVA_data<- participant_level %>% 
    select(ID, N2i_latency_LeftTarget, N2i_latency_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 


   Hemifield_ANOVA <- ezANOVA(data = ANOVA_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                        , within_covariates = NULL
                        , between = NULL
                        , between_covariates = NULL
                        , observed = NULL
                        , type = 3);
print("Repeated Measures ANOVA  for the effect of Hemifield on N2i_latency:")
print(Hemifield_ANOVA);

###################################################################
ANOVA_data<- participant_level %>% 
    select(ID, N2i_LeftTarget, N2i_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 


   Hemifield_ANOVA <- ezANOVA(data = ANOVA_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                        , within_covariates = NULL
                        , between = NULL
                        , between_covariates = NULL
                        , observed = NULL
                        , type = 3);
print("Repeated Measures ANOVA  for the effect of Hemifield on N2i Amplitude:")
print(Hemifield_ANOVA);


###################################################################
ANOVA_data<- participant_level %>% 
    select(ID, N2c_latency_LeftTarget, N2c_latency_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 


   Hemifield_ANOVA <- ezANOVA(data = ANOVA_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                        , within_covariates = NULL
                        , between = NULL
                        , between_covariates = NULL
                        , observed = NULL
                        , type = 3);
print("Repeated Measures ANOVA  for the effect of Hemifield on N2c_latency:")
print(Hemifield_ANOVA);

###################################################################
ANOVA_data<- participant_level %>% 
    select(ID, N2c_LeftTarget, N2c_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 


   Hemifield_ANOVA <- ezANOVA(data = ANOVA_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                        , within_covariates = NULL
                        , between = NULL
                        , between_covariates = NULL
                        , observed = NULL
                        , type = 3);
print("Repeated Measures ANOVA  for the effect of Hemifield on N2c Amplitude:")
print(Hemifield_ANOVA);


###################################################################
ANOVA_data<- participant_level %>% 
    select(ID, AlphaDesync_i_LeftTarget, AlphaDesync_i_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 


   Hemifield_ANOVA <- ezANOVA(data = ANOVA_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                        , within_covariates = NULL
                        , between = NULL
                        , between_covariates = NULL
                        , observed = NULL
                        , type = 3);
print("Repeated Measures ANOVA  for the effect of Hemifield on AlphaDesync_i:")
print(Hemifield_ANOVA);


###################################################################
ANOVA_data<- participant_level %>% 
    select(ID, AlphaDesync_c_LeftTarget, AlphaDesync_c_RightTarget) %>%
    na.omit() %>%
    gather(Hemifield, dv, -ID) 


   Hemifield_ANOVA <- ezANOVA(data = ANOVA_data
                          , dv = .(dv)
                          , wid = .(ID)
                          , within = .(Hemifield)
                        , within_covariates = NULL
                        , between = NULL
                        , between_covariates = NULL
                        , observed = NULL
                        , type = 3);
print("Repeated Measures ANOVA  for the effect of Hemifield on AlphaDesync_c:")
print(Hemifield_ANOVA);

```




#test correlation between all of the Asymmetry measures (i.e. RT, N2, CPP, alpha, asymmetry) 
```{r, echo=FALSE, warning=FALSE}
#Get the required data i.e. ID, and all the asymmeyry index measures

Asym_data_wide<-participant_level %>% select(., ID, contains("Asym"))

##Now grab only the Asym/lateralistion index measures 
data_for_cor<-select(Asym_data_wide, -ID)

##Re order the columns
# data_for_cor <- select(data_for_cor, RT_Asym, N2c_Asym, N2c_latency_Asym, N2i_Asym, N2i_latency_Asym, CPPonset_Asym, CPPslope_Asym, PreAlphaAsym)

##look at r-values, p-palues, and CIs  
print(corr.test(data_for_cor, method="pearson", adjust="none", alpha=.05,ci=TRUE),short=F)

cor_pram_list<-corr.test(data_for_cor, method="pearson", adjust="none", alpha=.05,ci=TRUE)

cor_pvalues<-as.data.frame(cor_pram_list$p)

#######################################
##Plot p-value matrix using ggplot:
png("P_values less than 05 uncorrected.png",  width = 10*600, height = 10*600, units = "px", res = 600)
p_data<-reshape2::melt(as.matrix(cor_pvalues))
p_data<-plyr::rename(p_data, c("value"="p_value"))
p_data<-dplyr::mutate(p_data, p_value = replace(p_value, p_value>.05, NA)) #only plot uncorected p-values less than .04
####Plot:
qplot(x=Var1, y=Var2, data=p_data, fill=p_value, geom="tile")+
    theme(axis.title.x = element_text(face="bold", size=9),
          axis.text.x  = element_text(face="bold", angle=-90,  size=9)) +
    theme(axis.title.y = element_text(face="bold", size=9),
          axis.text.y  = element_text(angle=0, vjust=0.5, size=9))
dev.off()

qplot(x=Var1, y=Var2, data=p_data, fill=p_value, geom="tile")+
    theme(axis.title.x = element_text(face="bold", size=9),
          axis.text.x  = element_text(face="bold", angle=-90,  size=9)) +
    theme(axis.title.y = element_text(face="bold", size=9),
          axis.text.y  = element_text(angle=0, vjust=0.5, size=9))
#######################################


cor_pvalues<-as.data.frame(cor_pram_list$p)
cor_pvalues<-cor_pvalues %>% tibble::rownames_to_column(.) %>%
  gather(var, val, - rowname) %>%
  spread(rowname, val)

#Make correlation matrix for corPlot()
cor_matrix<-cor(as.matrix(data_for_cor), use="na.or.complete")

#Save the corPlot() as a .png image
png("Correlation betweem RT_Asymmetry & SLF_Asymmetry.png",  width = 10*600, height = 10*600, units = "px", res = 600)
corPlot(cor_matrix, numbers=T, main="Correlation betweem RT_Asymmetry & SLF_Asymmetry",  show.legend=F, upper=T,  cex = 1)
dev.off()
corPlot(cor_matrix, numbers=T, main="Correlation betweem RT_Asymmetry & SLF_Asymmetry",  show.legend=F, upper=T,  cex = 1)


p1<-ggplot(data_for_cor, aes(x=RT_Asym, y=N2c_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region

p2<-ggplot(data_for_cor, aes(x=RT_Asym, y=N2c_latency_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
				
				

p3<-ggplot(data_for_cor, aes(x=RT_Asym, y=N2c_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
				
				
p4<-ggplot(data_for_cor, aes(x=RT_Asym, y=N2i_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
				
				

p5<-ggplot(data_for_cor, aes(x=RT_Asym, y=N2c_latency_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
				
				
p6<-ggplot(data_for_cor, aes(x=RT_Asym, y=CPPonset_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
				
				
p7<-ggplot(data_for_cor, aes(x=RT_Asym, y=CPPslope_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region

p8<-ggplot(data_for_cor, aes(x=N2c_Asym, y=CPPslope_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
				
				
p9<-ggplot(data_for_cor, aes(x=N2c_latency_Asym, y=CPPonset_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region



ggplot(data_for_cor, aes(x=RT_Asym, y=CPPonset_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region

ggplot(data_for_cor, aes(x=RT_Asym, y=PreAlphaAsym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region

ggplot(data_for_cor, aes(x=CPPonset_Asym, y=PreAlphaAsym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region

ggplot(data_for_cor, aes(x=CPPslope_Asym, y=AlphaDesync_i_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region

ggplot(data_for_cor, aes(x=CPPonset_Asym, y=AlphaDesync_c_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region


ggplot(data_for_cor, aes(x=CPPonset_Asym, y=CPPslope_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region


ggplot(data_for_cor, aes(x=RT_Asym, y=CPPslope_Asym)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
				

png("Some Scatter Plots.png",  width = 10*300, height = 10*300, units = "px", res = 600)				
source("multiplot.R")				
multiplot(p1,p2,p3,p4,p5,p6,p7,p8,p9, cols=3)
dev.off()
multiplot(p1,p2,p3,p4,p5,p6,p7,p8,p9, cols=3)


# plot(data_for_cor[,c(1:10)])


#Make histograms of all asymmetry_indexes
hist_data<-tidyr::gather(data_for_cor, measure, asymmetry_index, na.rm = T, convert = T, factor_key = T)
png("histograms of all asymmetry_indexes.png",  width = 10*600, height = 10*600, units = "px", res = 600)
ggplot(hist_data, aes(asymmetry_index))  + geom_histogram() + facet_wrap(~ measure, scales="free")
dev.off()
ggplot(hist_data, aes(asymmetry_index))  + geom_histogram() + facet_wrap(~ measure, scales="free")

```

#Look at 
```{r, echo=FALSE, warning=FALSE}



```


#Look at the effect of Hemifield on RT on a single trial level using linear mixed model

```{r, echo=FALSE, warning=FALSE}
data$Hemifield<-as.factor(data$Hemifield)

RT_random_effects_only<-lmer(log(RT) ~ 1 + (Hemifield | ID) +(1|ITI) + (1|Trial), data = data, REML=FALSE, na.action = na.omit)
RT_Hemifield<-update(RT_random_effects_only, .~. + Hemifield)
RT_TOT<-update(RT_Hemifield, .~. + Trial)
RT_Hemifield_by_TOT<-update(RT_TOT, .~. + Hemifield:Trial)
anova(RT_random_effects_only, RT_Hemifield, RT_Hemifield_by_TOT)

RT_PreAlphaPower<-update(RT_Hemifield_by_TOT, .~. + PreAlphaPower)
anova(RT_Hemifield_by_TOT, RT_PreAlphaPower)

# source("summarySE.R") 
# source("summarySEwithin.R") #function to calculate Std.Er of mean
# source("normDataWithin.R")
# plotdata <- summarySEwithin(data, measurevar="RT", withinvars=c("Hemifield"), idvar="ID")
# ggplot(plotdata, aes(x=Hemifield, y=RT, fill=Hemifield)) +
#     geom_bar(position=position_dodge(.9), colour="Black", stat="identity") + 
#     geom_errorbar(position=position_dodge(.9), width=.3, aes(ymin=RT-ci, ymax=RT+ci)) + #can change "se" to "ci" if I want to use 95%ci instead
#     geom_hline(yintercept=0) +  coord_cartesian(ylim = c(400, 600)) +
#     xlab("Hemifield") + ylab("RT (ms)") +
#     theme(axis.title.x = element_text(face="bold", size=12),
#           axis.text.x  = element_text(face="bold", angle=0,  size=12)) +
#     theme(axis.title.y = element_text(face="bold", size=12),
#           axis.text.y  = element_text(angle=0, vjust=0.5, size=12)) +
#     theme(legend.title = element_text(size=11, face="bold")) +
#     theme(legend.text = element_text(size = 11, face = "bold")) +
#     theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), axis.line = element_line(colour = "black")) 



# 
# #Look at a boxplot of log(RT)
# ggplot(data, aes(Hemifield, log(RT), colour = Hemifield))  + 
#     geom_boxplot() + coord_flip() + theme_bw ()


#Plot the effect of Hemifield*Time-on-task
ggplot(data, aes(x=data$Trial, y=data$RT,fill=Hemifield,colour=Hemifield)) +
     # stat_smooth(method="glm",level = 0.95,size=1) + # Add a glm smoothed fit curve with 95% confidence region around the three light conditions
    geom_smooth() +
    scale_fill_manual(name="Target\nHemifield",  breaks=c("Left", "Right"), labels=c(" Left", " Right"), guide = guide_legend(reverse=TRUE), values=c("#999999", "black")) +
    scale_colour_manual(name="Target\nHemifield",  breaks=c("Left", "Right"), labels=c(" Left", " Right"), guide = guide_legend(reverse=TRUE), values=c("black", "black")) +
    ylab("RT (ms)") +  xlab("Time On Task (trials)") + coord_cartesian(ylim = c(500, 700))+
    theme(axis.title.x = element_text(face="bold", size=14),
          axis.text.x  = element_text(face="bold", angle=0,  size=12)) +
    theme(axis.title.y = element_text(face="bold", size=14),
          axis.text.y  = element_text(angle=0, vjust=0.5, size=12)) +
    theme(legend.title = element_text(size=14, face="bold")) +
    theme(legend.text = element_text(size = 12, face = "bold")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
    panel.background = element_blank(), axis.line = element_line(colour = "black")) 

##Check the plot of the model parameters matches with this^ plot of the raw data 
# require(effects)
# plot(allEffects(RT_Hemifield_by_TOT), multiline=T)


```

**So this ^ shows that participants tended to react faster to left hemifield targets, but this leftward advangate decreased over time**


